### 2021-06-11 paper/paper.tex
update sythetic data

The main theoretical result for the cross entropy loss is that for a dataset with $n$ points,
the generalization error is $O(\sqrt{c/n})$.
There are many theorems that establish this result in different contexts.
The following is an example that relies on properties of SGD.
\begin{theorem}
\label{theorem:xentropy}
Assume that for all $i\in[n]$, $\ltwo{x_i} \le \rho$,
    and that for each class $i\in[c]$, $\ltwo{\w_i}\le B$.
Then the parameter vector $\bar W$ estimated from one epoch of SGD satisfies
\begin{equation}
    \E L_D(\bar W) - L_D(W^*) \le \frac {\sqrt cB\rho}{\sqrt n}
\end{equation}
where $W^* = \argmin L_D(W)$.
\end{theorem}
\begin{proof}
    \fixme{Write a proof of this result using Theorem 14.12 of Shalev-Shwartz and Ben-David and the properties of the cross entropy loss from the last set of notes.}
\end{proof}

@@

>>>>

The main theoretical result for the cross entropy loss is that for a dataset with $n$ points,
the generalization error is $O(\sqrt{c/n})$.
There are many theorems that establish this result in different contexts.
The following is an example that relies on properties of SGD.
\begin{theorem}
\label{theorem:xentropy}
Assume that for all $i\in[n]$, $\ltwo{x_i} \le \rho$,
    and that for each class $i\in[c]$, $\ltwo{\w_i}\le B$.
Then the parameter vector $\bar W$ estimated from one epoch of SGD satisfies
\begin{equation}
    \E L_D(\bar W) - L_D(W^*) \le \frac {\sqrt cB\rho}{\sqrt n}
\end{equation}
where $W^* = \argmin L_D(W)$.
\end{theorem}
\begin{proof}
    \fixme{Write a proof of this result using Theorem 14.12 of Shalev-Shwartz and Ben-David and the properties of the cross entropy loss from the last set of notes.}
    \begin{align}
    {\| W \|^2_F}&=\sum_{i=1}^c{\| W_i\|^2}\nonumber\\
                &\le\sum_{i=1}^c{B^2}\nonumber\\
                &\le cB^2\nonumber\\
   \| W \|_F  &\le \sqrt c B \nonumber
    \end{align}
Then we get:
    \begin{equation}
    l(\bar W)-l(W^*)\le\frac {\sqrt cB\rho}{\sqrt n}
    \end{equation}
   Take expectation of both side of equation(3):
   \begin{equation}
    \E L_D(\bar W) - L_D(W^*) \le \frac {\sqrt cB\rho}{\sqrt n}\nonumber
\end{equation}
\end{proof}

@@

Simloss is similarity based loss function which incorporates class similarities to support the training of neural network classifiers. Cross entropy loss assumes only one class is correct and punishes every misclassification, while Simloss indicates classes have similarities and classifying a target as a similar class is better. When calculating the loss function, instead of only taking the probability vector at the target index Simloss also adds the product of similarity between target and other classes and probability vector at the corresponding class. Non zero values of similarity matrix lead to smaller losses when the network gives a high score to classes similar to the correct one. It would allow the classifier to make less severe mistakes as it learns to predict similar classes.
\begin{align}
    L_{Simloss}&=-\frac{1}{N}\log(\sum_{c=1}^{C}S_{y_i,c}\cdot p_i[c])\\
    % L_{Simloss}=-\frac{1}{N}\log(\sum_{c=1}^{C}S_{y_i,c}\cdot\frac {\exp(-\trans\w_{y_i} \x)}{\sum_{j=1}^C \exp(-\trans \w_j \x)})
    p_i&=\frac {\exp(-\trans\w_{y_i} \x)}{\sum_{j=1}^C \exp(-\trans \w_j \x)}
\end{align}
